Parallel Multi-objective optimization using co-evolutionary islands and search space overlapping

### 2016-06-15 hpmoon-hpca.tex
Version to send

%\author{Pablo Garc\'ia-S\'anchez, Julio Ortega, Jes\'us Gonz\'alez, \\Pedro Angel Castillo and Juan Juli\'an Merelo\affilnum{1}}
\author{ANONYMOUS FOR BLIND REVIEW \affilnum{1}}
\affiliation{\affilnum{1} ANONYMOUS FOR BLIND REVIEW}
\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}

@@

However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the adaptive version (Table \ref{tab:results2048}), even improving the overlapping and disjoint methods. Therefore, there exist some kind of limit point in chromosome length where one method will be preferable to another, depending the number of islands, population size and length.

>>>>

%\author{Pablo Garc\'ia-S\'anchez, Julio Ortega, Jes\'us Gonz\'alez, \\Pedro Angel Castillo and Juan Juli\'an Merelo\affilnum{1}}
\author{ANONYMOUS FOR BLIND REVIEW \affilnum{1}}
\affiliation{\affilnum{1} ANONYMOUS FOR BLIND REVIEW}
%\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}

@@

However, with 2048 dimensions, results show that dividing the chromosome produces an improvement in all the quality indicators using the adaptive version (Table \ref{tab:results2048}), even improving the overlapping and disjoint methods. Therefore, there exist some kind of limit point in chromosome length where one method will be preferable to another, besides depending on the number of islands and population size.
